% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Bob(Xianglong) Jia}


\basicInfo{
  \email{jiaxianglong1987@gmail.com} \textperiodcentered\ 
  \phone{(+86) 137 6410 3386} \textperiodcentered\ 
  \linkedin[Bob(Xianglong) Jia]{https://www.linkedin.com/in/bob-xianglong-jia-6859b478}}


\section{\faUsers\ Coupang}
\datedsubsection{\textit{Principal Engineer, Supply Chain Management Automation}}{\textit{Oct.2017 -- Jun.2019}}
\textbf{Demand Forecasting} is the practice of predicting the future demand for stock keeping units to drive subsequent operations such as in-stock planning and the purchase orders placing.
\begin{itemize}
  \item Led the re-architecture of infrastructure and code base and reduced daily forecast run time by 91\%.
  \item Designed and implemented a forecast algorithm that improved production accuracy by 22\% - 26\%.
  \item Developed a generic big data analysis platform skeleton that enables rapid prototyping.
  \item Technology: Python, R, Scala, AWS(EC2, Redshift, S3), Spark, Mesos, Zeppelin
\end{itemize}

\datedsubsection{\textit{Senior Engineer, Platform}}{\textit{Sep.2016 -- Sep.2017}}
\textbf{API Dependency Monitor} reveals dependencies among micro-services by visualizing API invocations on aggregated level. It is also capable of detecting real-time performance anomalies without manually preset rules.
\begin{itemize}
  \item Designed and developed the core UI component of dependency and traffic visualization.
  \item Designed and developed the anomaly detection module with multidimensional Gaussian mixture model.
  \item Technology: Scala, D3.js, Angular2, Spark(MLlib)
\end{itemize}


\section{\faUsers\ Morgan Stanely}
\datedsubsection{\textit{Associate, Firm Risk Management IT}}{\textit{Apr.2013 -- Aug.2016}}
\smallskip

\textbf{SWORD} (Strategic Warehouse of Operational Relationship Data) serves as a source of information regarding operational service relationships between business units and legal entities.
\begin{itemize}
  \item Designed and developed the server side application.
  \item Trained junior engineers in business knowledge and programming best practices.
  \item Technology: Java, DB2, JavaScript
\end{itemize}


\textbf{FORCAST} (Firm Operational Risk Control Assessment Tracking) supports end-to-end administration of the Risk Control Self-Assessment process, which includes the creation of assessment, identification of further mitigation where appropriate, and recorded approval of assessments.
\begin{itemize}
  \item Took over the ownership of the project and enhanced the business logic implementation.
  \item Developed a utility to improve the maintainability of integration test code.
  \item Technology: Java, DB2, Flex
\end{itemize}

\textbf{REACTR} (Reference Data Activity Operational Risk) is a web application that enables the remapping of Operational Risk data items to accommodate the periodic organizational hierarchy changes.

\begin{itemize}
  \item Rewrote the data loading module and reduced time consumption by 87\%.
  \item Decreased the size of the code base by 35\% and increased test coverage from 0\% to 56\%.
  \item Technology: Java, DB2, Flex
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2010 -- 2013}
\textit{Master degree} in Software Engineering
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2006 -- 2010}
\textit{Bachelor degree} in Software Engineering

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, Scala, Java, JavaScript, SQL, Flex
  \item GitHub:\href{https://github.com/skinheadbob}{https://github.com/skinheadbob}
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
